How Well do we Teach Cybersecurity?\\(Abstract 20 January, Paper 27th)

### 2018-12-20 ITiCSE2019.tex
JHD updates during talk

Nevertheless, it is one thing to write curricula and requirements, and
another thing to deliver appropriate education, and one could
reasonably ask how well this is done in practice.

\section{Policy Context}

@@

The agreed Cybersecurity Principles and Learning Outcomes were included in the BCS Guidelines for accreditation in 2016. This resulted in an extended expectation of the coverage of Cybersecurity in programmes accredited by the Institute. The expectation is now that all students upon all accredited programmes will graduate with skills, knowledge and experience related to:

1. Information and risk
2. Threats and attacks
3. Cybersecurity architecture and operations
4. Secure systems and products
5. Cybersecurity management

This was discussed with the wider education community by a road-show lead by CPHC. (Alastair could you add something here?)

This change to the accreditation guidelines is now in an implementation period. The accreditation process adopted by the BCS is cyclic in nature. Formally the cycle is 5 years in duration. The new expectations have been implemented as follows. To ensure continuous accreditation,  accreditation visits are normally scheduled every 4 years. At the time of the next visit in this accreditation cycle accreditation is conditional upon a HEI having considered the guidelines and either adjusted the curriculum to meet the new expectations or have a formal plan in place for when and how adjustments will be made.  It is anticipate from 2020(?) the expectation will be all accredited programmes have the new expectations fully embedded.

>>>>

Nevertheless, it is one thing to write curricula and requirements, and
another thing to deliver appropriate education, and one could
reasonably ask how well this is done in practice.
\subsection{CyberSecurity: for all or for specialists?}
In one sense, this title is a false dichotomy: there is a serious need for cybersecurity specialists (estimates vary, but are always large), but also all in IT need to know \emph{some} CyberSecurity, as the recent fashion for talking about DevSecOps rather than just DevOps exemplifies.

AI: GDPR essentially expects CyberSecurity to be in all coding. 
JHD: PCI DSS insists on a Web Application Firewall, which is only needed if you don't trust your applications.

Specialist curricula abound: a recent one is \cite{ACM2017b}. However, given the shortage of specialists, in practice a good generalist with some CYberSecurity expertise can often get a ``specialist''.
\section{Policy Context}

@@

The agreed Cybersecurity Principles and Learning Outcomes were included in the BCS Guidelines for accreditation in 2016. This resulted in an extended expectation of the coverage of Cybersecurity in programmes accredited by the Institute. The expectation is now that all students upon all accredited programmes will graduate with skills, knowledge and experience related to:
\begin{enumerate}
\item Information and risk
\item Threats and attacks
\item Cybersecurity architecture and operations
\item Secure systems and products
\item Cybersecurity management
\end{enumerate}
This was discussed with the wider education community by a road-show lead by CPHC. (Alastair could you add something here?)

This change to the accreditation guidelines is now in an implementation period. The accreditation process adopted by the BCS is cyclic in nature. Formally the cycle is 5 years in duration. The new expectations have been implemented as follows. To ensure continuous accreditation,  accreditation visits are normally scheduled every 5 years. At the time of the next visit in this accreditation cycle accreditation is conditional upon a HEI having considered the guidelines and either adjusted the curriculum to meet the new expectations or have a formal plan in place for when and how adjustments will be made.  It is anticipate from 2020(?) the expectation will be all accredited programmes have the new expectations fully embedded.
